---
title: "Report"
author: "Guangkun Bao"
date: "2020/11/6"
output: html_document
---

```{r setup, include=FALSE}
Sys.setenv(LANG = "en")
knitr::opts_chunk$set(echo = TRUE)
```

# 5.3.3 Orstein–Uhlenbeck Process

## 1

In the Vasicek model of the Ornstein-Uhlenbeck process, 
$$r(t_{i+1}) = r(t_{i})e^{H(t_{i+1}) - H(t_{i})} + \mu(t_{i},t_{i+1}) + \sigma_{r}(t_{i},t_{i+1}) Z_{i+1},$$
 
where $t_{i+1} = t_{i}+\triangle$, 
$H(t_{i+1})-H(t_{i}) = -\alpha\triangle$, 
$\mu(t_{i},t_{i+1}) = b\alpha\int_{t_{i}}^{t_{i+1}}e^{-\alpha (t_{i+1}-s)}ds = b(1-e^{-\alpha\triangle})$,
$\sigma_{r}(t_{i},t_{i+1}) = \frac{\sigma}{\sqrt{2\alpha}}\sqrt{1-e^{-2\alpha\triangle}},$
$Z_{i+1} \sim N(0,1)$.

Let $t$ denotes $t_{i}$, $t+\triangle$ denotes $t_{i+1}$. Then
$$r(t+\triangle) = e^{-\alpha\triangle}r(t)+b(1-e^{-\alpha\triangle})+ \frac{\sigma}{\sqrt{2\alpha}}\sqrt{1-e^{-2\alpha\triangle}}Z,$$ 
where $Z\sim N(0,1)$.

## 2

```{r}
r0 = 1
T = 500
delta = 1/500

rou = function(alpha,sigma,b,r0,T,delta){ 
  r = c(r0)
  times = T/delta
  for(i in (1:times)){
    rt = r[i]
    p1 = exp(-alpha*delta) * rt
    p2 = b * (1-exp(-alpha*delta))
    p3 = sigma/sqrt(2*alpha) * (1-exp(-2*alpha*delta))^0.5
    z = rnorm(1)
    r[i+1] = p1+p2+p3*z
    }
  return(r)
}

```

I construct the 18 sample paths in one figure.
```{r}
par(mfrow=c(3,6))
for (alpha in c(0.1,1,5))
{for (sigma in c(0.1,0.2,0.5))
  {for (b in c(-5,5))
    {r = rou(alpha,sigma,b,r0 = 1,T = 500,delta = 1/500)
    plot(x=seq(0,T,by=1/500), y = r, main = '', xlab = 'time', ylab = 'sample')
      
    }
    
  }
}
```

From the plots above, it seems that when $\alpha$ increases, the path tends to be more steady, while when $\sigma$ increases, the path tends to be unstable.

## 3

Consider $\alpha=1$,$\sigma=0.5$,b=5,r$_{0}$ = 1.

```{r}
em = function(size,delta,alpha,sigma,b,r0){
  r1 = 0
  times = 1/delta
  for (i in (1:size)){
    rt = r0
    for (j in (1:times)){
      mean = rt + alpha * (b-rt) * delta
      sd = delta * sigma 
      rt = rnorm(n=1,mean=mean,sd=sd)
      }
    r1[i] = rt
  }
  return(r1)
}
```

When $\delta$ =1, the kernel density is 
```{r}
r1 = em(size = 1000, delta = 1, alpha = 1, sigma = 0.5, b = 5, 
        r0 = 1)
r1 = unlist(r1)
plot(density(r1),xlab = '',ylab = '',main = 'kernel density')
```
When $\delta$ =0.5, the kernel density is 
```{r}
r1 = em(size = 1000, delta = 0.5, alpha = 1, sigma = 0.5, b = 5, 
        r0 = 1)
r1 = unlist(r1)
plot(density(r1),xlab = '',ylab = '',main = 'kernel density')
```
When $\delta$ =0.1, the kernel density is 
```{r}
r1 = em(size = 1000, delta = 0.1, alpha = 1, sigma = 0.5, b = 5,
        r0 = 1)
r1 = unlist(r1)
plot(density(r1),xlab = '',ylab = '',main = 'kernel density')
```
When $\delta$ =0.01, the kernel density is 
```{r}
r1 = em(size = 1000, delta = 0.01, alpha = 1, sigma = 0.5, b = 5,
   r0 = 1)
r1 = unlist(r1)
plot(density(r1),xlab = '',ylab = '',main = 'kernel density')
```

# 5.3.4 Poisson Process

## 1

```{}
Integrate[t^(1/2)+E^(-t)*Sin[2*Pi* t], {t,0,5}]
```
By using mathematica we have 

$$Z =\int_{0}^{5} \sqrt{t}+e^{-t}sin(2\pi t)dt = 7.607738$$

Since it is a Poisson process, N(5) $\sim$ Poisson(Z).Therefore N(5) $\sim$ Poisson(7.6).

## 2

Simulation of a nonhomegeneous Poisson process with the thinning method

```{r}
rnhpp <- function(intensity, intmax, tmax) {
  n <- rpois(1, intmax)
  tt <- runif(n, 0, tmax)
  u <- runif(n)
  accept <- u < intensity(tt) / intmax
  sort(tt[accept])
}

intfun <- function(x) sqrt(x)+sin(2 * pi * x)*exp(-x)
```


## 3

Pool all the event points together as a sample and plot their kernel density. Overlay $\lambda(t) / \int_0^5 \lambda{s}ds$ with the kernel density.

```{r}
intmax = 10*sqrt(5)/3+(2*pi*(-1+exp(5)))/(exp(5)*(1+4*pi^2))
xx=unlist(replicate(1000, rnhpp(intfun, intmax, 5)))
plot(density(xx),xlab = '',ylab = '',main = '')

t=seq(0,5,0.005)
tt=intfun(t)/7.607738
par(new=TRUE)
plot(t,tt,type = 'l',col = 'red',xlab = '',ylab = '',axes = FALSE)
```